---
title: "Data Products Week 4 Project"
date: "June 28, 2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction
This presentation is part of the assignment for the Coursera *Developing Data Products* 
course. It will describe a Shiny application that can help identify the optimal feed type for 
chicks to maximize growth.

## Data
The data used for this project is from the `chickwts` data set. Newly hatched chicks were randomly allocated into six groups, and each group was given a different feed supplement. Their weights in grams after six weeks are given along with feed types. 

The data looks like:
```{r, comment="", echo=TRUE}
head(chickwts)
```

## How it works
In this app, one can select different types of feed supplements to visualize boxplots of associated chick weights. An example output:
```{r, message=FALSE, results="hide"}
library(ggplot2)
ggplot(chickwts, aes(x=feed, y=weight, color = feed)) +
        geom_boxplot() +
        geom_dotplot(binaxis='y', stackdir='center', dotsize=0.5) +
        xlab("Feed Type") + ylab("Weight (grams)")
```



## Summary
This app can be useful to quickly determine optimal feed type for chicks.  

* Shiny app can be found here:  
https://be-wang.shinyapps.io/courseraDataProductsApp/  

*  Github repository can be found here:  
https://github.com/be-wang/courseraDataProductsWeek4Project
